%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}
\usepackage{hyperref}
\PassOptionsToPackage{dvipsnames}{xcolor}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.5cm,right=9cm,marginparwidth=7.1cm,marginparsep=1.0cm,top=1.15cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{Mulberry}{HTML}{72243D}
\definecolor{SlateGrey}{gray}{0.005}
\definecolor{LightGrey}{gray}{0.2}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Sarthak Jain}
\tagline{Experiences in Industry Growth, Digital Marketing and EdTech}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
% \photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  
    \email{\color{blue} \href{mailto:sarthak.jain2404@gmail.com?Subject=Regarding Resume}{\small sarthak\Large.\small jain2404@gmail.com}}
    \phone{\color{blue}\href{tel:+917011189445}{\small +91 7011189445}}
%  \mailaddress{Address, Street, 00000 County}
%    \location{\color{blue}\href{https://www.google.com/maps/place/Delhi%/}{\small New Delhi}}
%  \homepage{marissamayr.tumblr.com/}
  \twitter{\color{blue}\href{https://twitter.com/sarcastic_sark/}{\small {@sarcastic\_sark}}}
    \linkedin{\color{blue}\href{https://www.linkedin.com/in/sarthak-jain24apr98/}{\small sarthak-jain24apr98}}
    \github{\color{blue}\href{https://github.com/sarthak-1998}{\small sarthak-1998}} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[SideBar]{\Large Professional Experience}

\cvevent{\color{blue}\href{https://codingblocks.com/team.html}{Digital Marketing Executive and Test Engineer}}{\color{blue}\href{https://codingblocks.com}{Coding Blocks}}{Nov2018-Ongoing}{Delhi, India}
\begin{itemize}
\item Spearheaded the adoption of new methodologies in company to bring in real-time data monitoring, trace-ability and achieve compliance. 
\item Consistently tested CB Online App and website for bugs.
\item Researched and pursued new business campaigns for the growth of the business resulted in 1500 times increase in user sign-ups.
\item Increased social media audience and engagement along with site SEO by multiple folds, furthermore managed online adverts.
\item Organized workshops \& Hackathons at colleges and Universities in collaboration with communities across India, furthermore mentored community of over 400 Campus Ambassadors.
\end{itemize}


\cvevent{Web Developer Intern}{\color{blue}\href{https://allindiaradio.gov.in/}{All India Radio (AIR), Prasar Bharati}}{June2018-July2018 }{New Delhi, India}
\begin{itemize}
\item Maintained and Created a wonderful website to digitizes the Complaint filing System for the Government quarter residents. 
\item Constantly updated and Monitored the company’s database systems.

\end{itemize}


\cvevent{Social Media Manager}{\color{blue}\href{https://www.shopnani.com/}{ ShopNani }}{Dec2016-Jan2017 }{New Delhi, India}

\begin{itemize}
\item Wrote niche articles on latest prevailing Tech news for the website, Blog and social media accounts for daily postings.
Evaluated different insights and Demographics. Handled the company’s online presence.
 \item Monitored ongoing marketing campaigns
Increased social media following and clicks by 200\%

\end{itemize}


\cvsection{\Large  Projects}
\cvproject{\color{blue}\href{https://sarthakj.me}{Website sarthakj.me - \color{black}Node.js}}
\begin{itemize}
\item My interactive Website hosted on AWS.
\end{itemize}

\cvproject{\color{blue}\href{https://github.com/sarthak-1998/Rap-Generator}{Lyrics Generator - \color{black}Python}}
\begin{itemize}
\item A Markov Chain based Machine Learning model to generate song lyrics. 
\end{itemize}

%\cvproject{\color{blue}\href{https://github.com/sarthak-1998/Parking%-Lot-Problem}{Parking Lot App - \color{black}Ruby}}
%\begin{itemize}
%\item Parking lot terminal based application for effective parking %solutions.
%\end{itemize}

%\cvproject{\color{blue}\href{https://github.com/sarthak-1998/codingblocks.com}{Coding Blocks Website - \color{black}VanillaJS}}
%\begin{itemize}
%\item The Coding Blocks main website.
%\end{itemize}

%\cvproject{\color{blue}\href{https://github.com/sarthak-1998/shortlr2-backend}{Short Link Generator - \color{black}Node.js}}
%\begin{itemize}
%\item Short link generator with additional features such as use UTM tracking.
%\end{itemize}

%\cvproject{\color{blue}\href{https://github.com/sarthak-1998/LIVE-Code-Share}{Live Code Share - \color{black}Node.js}}
%\begin{itemize}
%\item Web app to support Live Code sharing \& chatting feature.
%\end{itemize}


\cvproject{\color{blue}\href{https://github.com/sarthak-1998/RWA-WebApp-AIR}{Web App for AIR - \color{black}C\# and ASP.Net}}
\begin{itemize}
\item This is the logistic application developed to digitize the manual filing of complaints and their status tracking for Government quarters.
\end{itemize}


\cvsection{\Large Education}
\cvevent{\small{B.Tech - Computer Science }}
{\small{Maharaja Agrasen Institute of Technology}}
{ Aug 2016 -- May 2020 \hspace{1cm} CGPA: 7.43 }{}
\cvevent{\small{Senior Secondary Education- 12th (CBSE)}}{\small{Kendriya Vidyalaya sector-8 Rohini, Delhi}}{2016 \hspace{1cm} Percentage: 90.2}{} 
\cvevent{\small{Secondary Education-10th (CBSE)}}{\small{Kendriya Vidyalaya sector-8 Rohini, Delhi}}{
2014 \hspace{1cm} CGPA: 10}{}



%\cvsection{\Large Personal Skills}

%\cvtag {Creative spirit}
%\cvtag{Reliable and professional}
%\cvtag{Organized} \newline
%\cvtag{Punctual}
%\cvtag{Team player}
%\cvtag{Fast learner}
%\cvtag{Motivated} 

%\cvskill {fqfmf}{3} 

%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
